---
title: "Cluster Analysis Clean"
author: "Rob Patro"
date: "5/27/2021"
output: 
    html_document:
        keep_md: true
---

This script is used for testing the effect of different cell filtering strategies on the clustering results and generating the figures in Supplementary section S6.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Functions used in the analysis 

```{r}
suppressPackageStartupMessages({
    library(devtools)
    library(ggplot2)
    library(SingleCellExperiment)
    library(Seurat)
    library(Matrix)
    library(DropletUtils)
})
set.seed(1234)
dir.create("figures",recursive = TRUE, showWarnings = FALSE)

```


```{r}
#' Read alevin-fry quantifications into a SingleCellExperiment object
load_fry <- function(frydir, which_counts = c('S', 'A'), verbose = FALSE) {
  suppressPackageStartupMessages({
    library(rjson)
    library(Matrix)
    library(SingleCellExperiment)
  })
  
  # read in metadata
  meta_info <- fromJSON(file = file.path(frydir, "meta_info.json"))
  ng <- meta_info$num_genes
  usa_mode <- meta_info$usa_mode
  
  if (usa_mode) {
    if (length(which_counts) == 0) {
      stop("Please at least provide one status in 'U' 'S' 'A' ")
    }
    if (verbose) {
      message("processing input in USA mode, will return ", paste(which_counts, collapse = '+'))
    }
  } else if (verbose) {
    message("processing input in standard mode, will return spliced count")
  }

  # read in count matrix
  af_raw <- readMM(file = file.path(frydir, "alevin", "quants_mat.mtx"))
  # if usa mode, each gene gets 3 rows, so the actual number of genes is ng/3
  if (usa_mode) {
    if (ng %% 3 != 0) {
      stop("The number of quantified targets is not a multiple of 3")
    }
    ng <- as.integer(ng/3)
  }
  
  # read in gene name file and cell barcode file
  afg <- read.csv(file.path(frydir, "alevin", "quants_mat_cols.txt"), 
                  strip.white = TRUE, header = FALSE, nrows = ng, 
                  col.names = c("gene_ids"), row.names = 1)
  afc <- read.csv(file.path(frydir, "alevin", "quants_mat_rows.txt"), 
                  strip.white = TRUE, header = FALSE,
                  col.names = c("barcodes"), row.names = 1)

  # if in usa_mode, sum up counts in different status according to which_counts
  if (usa_mode) {
    rd <- list("S" = seq(1, ng), "U" =  seq(ng + 1, 2 * ng),
               "A" =  seq(2 * ng + 1, 3 * ng))
    o <- af_raw[, rd[[which_counts[1]]], drop = FALSE]
    for (wc in which_counts[-1]) {
      o <- o + af_raw[, rd[[wc]], drop = FALSE]
    }
  } else {
    o <- af_raw
  }
  
  # create SingleCellExperiment object
  sce <- SingleCellExperiment(list(counts = t(o)),
                              colData = afc,
                              rowData = afg
  )
  sce
}
```


```{r}
get_clusters <- function(seurat_obj, do_scale=TRUE) {
  seurat_obj[["percent.mt"]] <- PercentageFeatureSet(seurat_obj, pattern = "^mt-")
  violin_plot <- VlnPlot(seurat_obj, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
  plot1 <- FeatureScatter(seurat_obj, feature1 = "nCount_RNA", feature2 = "percent.mt")
  plot2 <- FeatureScatter(seurat_obj, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")
  feat_plot <- plot1 + plot2
  
  seurat_obj_filt <- subset(seurat_obj, subset = nFeature_RNA < 6000 & nCount_RNA < 25000)
  seurat_obj_filt <- subset(seurat_obj_filt, subset = nFeature_RNA > 200 & nCount_RNA < 15000 & percent.mt < 30)
  
  seurat_obj_filt <- NormalizeData(seurat_obj_filt, normalization.method = "LogNormalize", scale.factor = 10000)

  seurat_obj_filt <- FindVariableFeatures(seurat_obj_filt, selection.method = "vst", nfeatures = 2000)
  
  all.genes <- rownames(seurat_obj_filt)
 
  seurat_obj_filt <- ScaleData(seurat_obj_filt, features = all.genes, do.scale=do_scale)
  
  seurat_obj_filt <- RunPCA(seurat_obj_filt, features = VariableFeatures(object = seurat_obj_filt))
  pca_plot <- DimPlot(seurat_obj_filt, reduction = "pca")

  seurat_obj_filt <- FindNeighbors(seurat_obj_filt, dims = 1:20)
  
  seurat_obj_filt_0.9 <- FindClusters(seurat_obj_filt, resolution = 0.9)
  seurat_obj_filt_1.2 <- FindClusters(seurat_obj_filt, resolution = 1.2)
  
  seurat_obj_filt_0.9 <- RunTSNE(seurat_obj_filt_0.9, dims = 1:20)
  seurat_obj_filt_1.2 <- RunTSNE(seurat_obj_filt_1.2, dims = 1:20)
  
  tsne0.9 <- DimPlot(seurat_obj_filt_0.9, reduction = "tsne", label=TRUE,repel=TRUE) + theme(axis.title.y = element_blank(), axis.title.x = element_blank())
  tsne1.2 <- DimPlot(seurat_obj_filt_1.2, reduction = "tsne", label=TRUE,repel=TRUE) + theme(axis.title.y = element_blank(), axis.title.x = element_blank())
  
  # seurat_obj_filt_0.9.markers <- FindAllMarkers(seurat_obj_filt_0.9, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)    
  # seurat_obj_filt_1.2.markers <- FindAllMarkers(seurat_obj_filt_1.2, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
  
  feat_genes <- c("exorh", "gnat1", "gngt1", "gnat2", "gngt2a", "col14a1b", "opn1lw1", "parietopsin", "asip2b", "rpe65a", "dkk3b", 
                  "fabp7b", "elavl4", "cart3", "gng8", "kiss1", "dcn", "igfbp5b", "cahz", "hbaa1", "ccr9a", "il4", "cd74a", "apoc1", 
                  "kdrl", "plvapa", "epcam", "icn2")
  dotplot_0.9 <- DotPlot(object = seurat_obj_filt_0.9, dot.scale = 3, features = feat_genes) + theme(axis.text.x = element_text(angle = 50, hjust = 1, vjust = 1), axis.title.y = element_blank(), axis.title.x = element_blank())
  dotplot_1.2 <- DotPlot(object = seurat_obj_filt_1.2, dot.scale = 3, features = feat_genes) + theme(axis.text.x = element_text(angle = 50, hjust = 1, vjust = 1), axis.title.y = element_blank(), axis.title.x = element_blank())
  
  retlist <- list("violin_plot" = violin_plot, 
                  "feat_plot" = feat_plot, 
                  "pca_plot" = pca_plot, 
                  "tsne0.9" = tsne0.9,
                  "tsne1.2" = tsne1.2, 
                  "dotplot0.9" = dotplot_0.9, 
                  "dotplot1.2" = dotplot_1.2, 
                  "obj0.9" = seurat_obj_filt_0.9, 
                  "obj1.2" = seurat_obj_filt_1.2
                  # ,"markers0.9" = seurat_obj_filt_0.9.markers
                  # ,"markers1.2" = seurat_obj_filt_1.2.markers
                  )
  return(retlist) 
}
```

```{r}
filter_empty <- function(unfiltered_sce, lower=100) {
  br.out <- barcodeRanks(counts(unfiltered_sce))
  e.out <- emptyDrops(counts(unfiltered_sce), lower=lower)
  is.cell <- e.out$FDR <= 0.01
  is.cell[is.na(is.cell)] <- FALSE
  sum(is.cell, na.rm=TRUE)
  filtered_sce <- unfiltered_sce[,is.cell]
  seu <- CreateSeuratObject(counts(filtered_sce), min.cells = 3, min.feature = 200)
  return(seu)
}
```

```{r}
filter_empty_shainer <- function(sce) {
  # parameters / method taken from https://github.com/mstemmer/kb-helper/blob/main/kb_data_to_seurat.Rmd
  tot_counts <- colSums(counts(sce))
  summary(tot_counts)
  bc_rank <- barcodeRanks(counts(sce), lower = 500)
   
  # Remove genes that are not detected and empty droplets
  sce <- sce[, tot_counts > metadata(bc_rank)$inflection]
  dim(sce) # use print() to show output in a for loop
  
  seu <- CreateSeuratObject(counts(sce), min.cells = 3, min.feature = 200)
  return(seu)
}
```


```{r}
gid_to_gname <- read.table('dr_gid_to_gname_fixed.tsv')
```

```{r}
fix_gene_names <- function(sce, gid_to_gname, strip_version=FALSE) {
  if (strip_version) {
    rownames(sce) <- sub("\\.\\d+", "", rownames(sce))
  }
  rownames(sce) <- gid_to_gname$V2[match(rownames(sce), gid_to_gname$V1)]
  return(sce)
}
```

```{r}
load_kb_matrix <- function(matdir) {
  
  bcp <- file.path(matdir, "cells_x_genes.barcodes.txt")
  gnp <- file.path(matdir, "cells_x_genes.genes.txt")
  mp <- file.path(matdir, "cells_x_genes.mtx")
  
  kbc <- read.csv(bcp, strip.white = TRUE, header = FALSE,
                  col.names = c("barcodes"), row.names = 1)
  genes <- read.csv(gnp, strip.white = TRUE, header = FALSE,
                  col.names = c("barcodes"), row.names = 1)
  kbm <- readMM(mp)
  kbme <- SingleCellExperiment(list(counts=t(kbm)), rowData=genes, colData=kbc)
  return(kbme)
}
```


```{r}
feat_genes <- c("exorh", "gnat1", "gngt1", "gnat2", "gngt2a", "col14a1b", "opn1lw1", "parietopsin", "asip2b", "rpe65a", "dkk3b", 
                "fabp7b", "elavl4", "cart3", "gng8", "kiss1", "dcn", "igfbp5b", "cahz", "hbaa1", "ccr9a", "il4", "cd74a", "apoc1", 
                "kdrl", "plvapa", "epcam", "icn2")
```


## Shainer et al. 


Process the alevin-fry output.

```{r, results='hide'}
set.seed(1234)

quant_sa_unfilt <- load_fry('fry_results/fry_unfilt_quant_usa_cr-like', which_counts=c('S','A'))
quant_sa_unfilt <- fix_gene_names(quant_sa_unfilt, gid_to_gname)
af_sa_unfilt_shainer <- filter_empty_shainer(quant_sa_unfilt)
ncol(af_sa_unfilt_shainer)
af_sa_unfilt_original_res <- get_clusters(af_sa_unfilt_shainer)
```


### alevin-fry dot-plot at resolution 0.9

```{r}
af_sa_unfilt_original_res$dotplot0.9
```


```{r}
af_sa_unfilt_original_res$obj0.9 <- RenameIdents(af_sa_unfilt_original_res$obj0.9,
`0` = "rod-like PhR",
`1` = "rod-like PhR",
`4` = "rod-like PhR" ,
`9` = "rod-like PhR",
`16` = "rod-like PhR",
`20` = "rod-like PhR",

`15` = "red cone PhR",
`18` =  "PT cone PhR" ,

`3` = "RPE-like" ,
`5` = "RPE-like",

`7` = "Muller glia-like" ,

`13` = "neurons",

`8` = "habenula neurons (gng8)",

`2` = "habenula neurons (kiss1)",
`10` = "habenula neurons (kiss1)",
`19` = "habenula neurons (kiss1)",

`6` = "fibroblasts",

`11` = "erythrocytes",

`12` = "leukocytes",

`14` = "microglia/macrhophages",

`17` = "vascular endothelial cells",

`21` = "epithelial cells")
levels(af_sa_unfilt_original_res$obj0.9) <- c("rod-like PhR", "red cone PhR", "PT cone PhR", "RPE-like", "Muller glia-like", "neurons", "habenula neurons (gng8)", "habenula neurons (kiss1)",
                                          "fibroblasts", "erythrocytes", "leukocytes", "microglia/macrhophages", "vascular endothelial cells", "epithelial cells")
af_sa_unfilt_original_res$dotplot0.9 <- DotPlot(object = af_sa_unfilt_original_res$obj0.9, dot.scale = 3, features = feat_genes) + theme(axis.text.x = element_text(angle = 50, hjust = 1, vjust = 1),axis.text.y = element_text(size = 24), axis.title.y = element_blank(), axis.title.x = element_blank())
af_sa_unfilt_original_res$dotplot0.9
```


```{r}
af_sa_unfilt_original_res$tsne0.9 <- DimPlot(af_sa_unfilt_original_res$obj0.9, reduction = "tsne", label=TRUE,repel=TRUE) # + theme(axis.title.y = element_blank(), axis.title.x = element_blank())
af_sa_unfilt_original_res$tsne0.9 
```



## emptyDrops


Process the alevin-fry output.

```{r, results='hide'}
set.seed(1234)

quant_sa_unfilt <- load_fry('fry_results/fry_unfilt_quant_usa_cr-like', which_counts=c('S','A'))
quant_sa_unfilt <- fix_gene_names(quant_sa_unfilt,gid_to_gname)
af_sa_unfilt_filt <- filter_empty(quant_sa_unfilt)
ncol(af_sa_unfilt_filt)
af_sa_unfilt_filt_res <- get_clusters(af_sa_unfilt_filt)
```


### alevin-fry dot-plot at resolution 0.9

```{r}
af_sa_unfilt_filt_res$dotplot0.9
```



```{r}
af_sa_unfilt_filt_res$obj0.9 <- RenameIdents(af_sa_unfilt_filt_res$obj0.9,
`0` = "rod-like PhR",
`1` = "rod-like PhR",
`10` = "rod-like PhR",
`16` = "rod-like PhR",
`18` = "rod-like PhR",

`13` = "cone PhR",

`2` = "RPE-like",
`4` = "RPE-like",

`7` = "Muller glia-like",
`12` = "Muller glia-like",

`14` = "neurons",

`8` =  "habenula neurons (gng8)",

`3` = "habenula neurons (kiss1)",
`9` = "habenula neurons (kiss1)",

`5` = "fibroblasts",

`6` = "erythrocytes",

`11` = "leukocytes",
`19` = "leukocytes",

`15` = "microglia/macrhophages",



`17` = "vascular endothelial cells",

`20` = "epithelial cells"


)
levels(af_sa_unfilt_filt_res$obj0.9) <- c("rod-like PhR", "cone PhR", "RPE-like", "Muller glia-like", "neurons", "habenula neurons (gng8)", "habenula neurons (kiss1)",
                                          "fibroblasts", "erythrocytes", "leukocytes", "microglia/macrhophages", "vascular endothelial cells", "epithelial cells")
af_sa_unfilt_filt_res$dotplot0.9 <- DotPlot(object = af_sa_unfilt_filt_res$obj0.9, dot.scale = 3, features = feat_genes) + theme(axis.text.x = element_text(angle = 50, hjust = 1, vjust = 1),axis.text.y = element_text(size = 24), axis.title.y = element_blank(), axis.title.x = element_blank())
af_sa_unfilt_filt_res$dotplot0.9
```


```{r}
af_sa_unfilt_filt_res$tsne0.9 <- DimPlot(af_sa_unfilt_filt_res$obj0.9, reduction = "tsne", label=TRUE,repel=TRUE) #+ theme(axis.title.y = element_blank(), axis.title.x = element_blank())
af_sa_unfilt_filt_res$tsne0.9 
```


## fry knee


Load alevin-fry first to get the cell set

```{r, results='hide'}
set.seed(1234)

af_sa_knee <- load_fry('fry_results/fry_knee_quant_usa_cr-like', which_counts=c('S','A'))
af_sa_knee <- fix_gene_names(af_sa_knee,gid_to_gname)
af_sa_knee_obj <- CreateSeuratObject(counts(af_sa_knee), min.cells = 3, min.feature = 200)
ncol(af_sa_knee_obj)
af_sa_knee_res <- get_clusters(af_sa_knee_obj)
```


### alevin-fry (knee) dot-plot at resolution 0.9

```{r}
af_sa_knee_res$dotplot0.9
```


```{r}
af_sa_knee_res$obj0.9 <- RenameIdents(af_sa_knee_res$obj0.9,
`0` = "rod-like PhR",
`1` = "rod-like PhR",
`2` = "rod-like PhR",
`10` = "rod-like PhR",
`19` = "rod-like PhR",

`15` = "red cone PhR",
`16` = "PT cone PhR",

`3` = "RPE-like",
`5` = "RPE-like",

`8` = "Muller glia-like",

`12` = "neurons",

`7` =  "habenula neurons (gng8)",

`4` = "habenula neurons (kiss1)",
`9` = "habenula neurons (kiss1)",
`18` = "habenula neurons (kiss1)",

`6` = "fibroblasts",

`11` = "erythrocytes",

`14` = "leukocytes",

`13` = "microglia/macrhophages",

`17` = "vascular endothelial cells",

`20` = "epithelial cells"

)
levels(af_sa_knee_res$obj0.9) <- c("rod-like PhR", "red cone PhR","PT cone PhR", "RPE-like", "Muller glia-like", "neurons", "habenula neurons (gng8)", "habenula neurons (kiss1)",
                                          "fibroblasts", "erythrocytes", "leukocytes", "microglia/macrhophages", "vascular endothelial cells", "epithelial cells")
af_sa_knee_res$dotplot0.9 <- DotPlot(object = af_sa_knee_res$obj0.9, dot.scale = 3, features = feat_genes) + theme(axis.text.x = element_text(angle = 50, hjust = 1, vjust = 1),axis.text.y = element_text(size = 24), axis.title.y = element_blank(), axis.title.x = element_blank())
af_sa_knee_res$dotplot0.9
```


```{r}
af_sa_knee_res$tsne0.9 <- DimPlot(af_sa_knee_res$obj0.9, reduction = "tsne", label=TRUE,repel=TRUE) + theme(axis.title.y = element_blank(), axis.title.x = element_blank())
af_sa_knee_res$tsne0.9 
```

## Venn on cell filtering strategies

```{r}
# install.packages("ggVennDiagram")
library(ggVennDiagram)

l = list("original_y" = colnames(af_sa_unfilt_shainer),
          "ed_n" = colnames(af_sa_unfilt_filt),
          "knee_y" = colnames(af_sa_knee_obj)
         )

ggVennDiagram(l)

```

```{r}
pdf(file = "superset_figures/venn_selected_cells_diff_cell_filtering.pdf",   # The directory you want to save the file in
    width = 8, # The width of the plot in inches
    height = 8) # The height of the plot in inches

ggVennDiagram(l)

# Step 3: Run dev.off() to create the file!
dev.off()
```



```{r}
original_gene_act = rowSums(af_sa_unfilt_shainer@assays$RNA@counts  > 0)
length(original_gene_act)
sum(original_gene_act != 0)
```

```{r}
ed_gene_act = rowSums(af_sa_unfilt_filt@assays$RNA@counts  > 0)
length(ed_gene_act)
sum(ed_gene_act != 0)
```


```{r}
knee_gene_act = rowSums(af_sa_knee_obj@assays$RNA@counts  > 0)
length(knee_gene_act)
sum(knee_gene_act != 0)
```




```{r}
# install.packages("ggVennDiagram")
library(ggVennDiagram)

l = list("original_y" = names(original_gene_act[original_gene_act != 0]),
          "ed_n" = names(ed_gene_act[ed_gene_act != 0]),
          "knee_y" = names(knee_gene_act[knee_gene_act != 0])
         )

ggVennDiagram(l)

```


```{r}
pdf(file = "superset_figures/venn_expressed_genes_all_cells_diff_cell_filtering.pdf",   # The directory you want to save the file in
    width = 8, # The width of the plot in inches
    height = 8) # The height of the plot in inches

ggVennDiagram(l)

# Step 3: Run dev.off() to create the file!
dev.off()
```


## PHR clusters in different cell filtering strategies.


### Shainer

```{r}
cb_original_red_phr = colnames(af_sa_unfilt_original_res$obj0.9)[af_sa_unfilt_original_res$obj0.9@active.ident == "red cone PhR"]
cb_original_pt_phr = colnames(af_sa_unfilt_original_res$obj0.9)[af_sa_unfilt_original_res$obj0.9@active.ident == "PT cone PhR"]

cb_original_red_phr
```

```{r}
cb_original_pt_phr
```

### ed

```{r}
cb_ed_cone_phr = colnames(af_sa_unfilt_filt_res$obj0.9)[af_sa_unfilt_filt_res$obj0.9@active.ident == "cone PhR"]

cb_ed_cone_phr
```

### knee



```{r}
cb_knee_red_phr = colnames(af_sa_knee_res$obj0.9)[af_sa_knee_res$obj0.9@active.ident == "red cone PhR"]
cb_knee_pt_phr = colnames(af_sa_knee_res$obj0.9)[af_sa_knee_res$obj0.9@active.ident == "PT cone PhR"]

cb_knee_red_phr
```

```{r}
cb_knee_pt_phr
```

```{r}

l = list("original_y" = c(cb_original_pt_phr, cb_original_red_phr),
          "ed_n" = cb_ed_cone_phr,
          "knee_y" = c(cb_knee_pt_phr, cb_knee_red_phr)
         )

ggVennDiagram(l)

```

```{r}
pdf(file = "superset_figures/venn_cone_cells_diff_cell_filtering.pdf",   # The directory you want to save the file in
    width = 8, # The width of the plot in inches
    height = 8) # The height of the plot in inches

ggVennDiagram(l)

# Step 3: Run dev.off() to create the file!
dev.off()
```


## HVG

### shainer

```{r}
gene_original_red_cone = FindMarkers(af_sa_unfilt_original_res$obj0.9,ident.1 = "red cone PhR", only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
gene_original_red_cone = rownames(gene_original_red_cone)[gene_original_red_cone$p_val_adj < 0.05]
gene_original_pt_cone = FindMarkers(af_sa_unfilt_original_res$obj0.9,ident.1 = "PT cone PhR", only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
gene_original_pt_cone = rownames(gene_original_pt_cone)[gene_original_pt_cone$p_val_adj < 0.05]

gene_original_pt_vs_red = FindMarkers(af_sa_unfilt_original_res$obj0.9,ident.1 = "PT cone PhR", ident.2 = "red cone PhR", only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
gene_original_pt_vs_red = rownames(gene_original_pt_vs_red)[gene_original_pt_vs_red$p_val_adj < 0.05]

```

### ed

```{r}
gene_ed_cone = FindMarkers(af_sa_unfilt_filt_res$obj0.9,ident.1 = "cone PhR", only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
gene_ed_cone = rownames(gene_ed_cone)[gene_ed_cone$p_val_adj < 0.05]

```

### knee

```{r}
gene_knee_red_cone = FindMarkers(af_sa_knee_res$obj0.9,ident.1 = "red cone PhR", only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
gene_knee_red_cone = rownames(gene_knee_red_cone)[gene_knee_red_cone$p_val_adj < 0.05]

gene_knee_pt_cone = FindMarkers(af_sa_knee_res$obj0.9,ident.1 = "PT cone PhR", only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
gene_knee_pt_cone = rownames(gene_knee_pt_cone)[gene_knee_pt_cone$p_val_adj < 0.05]

gene_knee_pt_vs_red = FindMarkers(af_sa_knee_res$obj0.9,ident.1 = "PT cone PhR", ident.2 = "red cone PhR", only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
gene_knee_pt_vs_red = rownames(gene_knee_pt_vs_red)[gene_knee_pt_vs_red$p_val_adj < 0.05]
```




```{r}

l = list("original_red" = gene_original_red_cone,
          "original_pt" = gene_original_pt_cone,
          "ed_cone" = gene_ed_cone
         )

ggVennDiagram(l)

```


```{r}

l = list("knee_red" = gene_knee_red_cone,
          "knee_pt" = gene_knee_pt_cone,
          "ed_cone" = gene_ed_cone
         )

ggVennDiagram(l)

```

```{r}

l = list("original_red" = gene_original_red_cone,
          "original_pt" = gene_original_pt_cone,
         "knee_red" = gene_knee_red_cone,
          "knee_pt" = gene_knee_pt_cone
         )

ggVennDiagram(l)

```

```{r}
library(UpSetR)

all_g = unique(c(gene_ed_cone,
                  gene_knee_pt_cone,
                  gene_knee_red_cone,
                  gene_original_pt_cone,
                  gene_original_red_cone
                  )
                )

df = data.frame(matrix(0, nrow = length(all_g),
                       ncol = 5
                       )
                )
colnames(df) = c("original_red", "original_pt", "ed_cone", "knee_red","knee_pt")

rownames(df) = all_g

df[gene_original_red_cone,"original_red"] = 1
df[gene_original_pt_cone,"original_pt"] = 1
df[gene_ed_cone,"ed_cone"] = 1
df[gene_knee_pt_cone,"knee_pt"] = 1
df[gene_knee_red_cone,"knee_red"] = 1



us = upset(df, nsets = 5, nintersects = 100, mb.ratio = c(0.5, 0.5),
      order.by = c("freq", "degree"), decreasing = c(TRUE,FALSE),mainbar.y.label = "# ovelapping genes", sets.x.label = "# HVG",text.scale = 2)

us
```


```{r}
pdf(file = "superset_figures/superset_diff_cell_filtering.pdf",   # The directory you want to save the file in
    width = 12, # The width of the plot in inches
    height = 8) # The height of the plot in inches

us
# Step 3: Run dev.off() to create the file!
dev.off()
```



```{r}
upset(df, sets = c("ed_cone", "knee_pt", "original_pt"), nintersects = 30, mb.ratio = c(0.5, 0.5),
      order.by = c("freq", "degree"), decreasing = c(TRUE,FALSE),mainbar.y.label = "# ovelapping genes", sets.x.label = "# HVG")

```















